Lemma 1

### 2021-04-07 notes/jessie-russian-lemma.tex
I have no idea what is going on in the proof of Lemma 2

Now define functions $P_m : \Y \to \reals^d$ so that $P_m(y) = \int_E V_m(y') dpy'$, where $E =\{y' \in \Y \mid y' \leq y\}$ and $P_m(y)$ is the CDF of $V_m$.  We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.
We have uniform boundedness from their first past of the result, and monotonicity from each $P_m$ being a CDF

>>>>

Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?}
We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.
